%-------------------------
% Author : Thang Pham
%------------------------

% Acknowledge: the below resume is based on sb2nov's resume
% repo in "https://github.com/sb2nov/resume"

\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt} ]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\linkDesc}[1]{\underline{\texttt{#1}}}

\newcommand{\resumeItem}[2]{
  \item\small{#1{: #2}} \vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2} \vspace{-2pt}}

\newcommand{\resumeDescItem}[1]{\item[-]\small{#1} \vspace{-2pt}}
\newcommand{\resumeDescItemNoBullet}[1]{\item[]\small{#1} \vspace{-2pt}}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeListStart}{\vspace{-2pt}\begin{itemize}[leftmargin=*]}
\newcommand{\resumeListEnd}{\end{itemize}}

\renewcommand{\labelitemii}{$\circ$}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \LARGE\textbf{Thang Pham}
  & \faIcon{mobile-alt} (+1) 226-507-5123\\
  \href{https://github.com/aome510}{\faIcon{github} aome510}
  \href{https://www.linkedin.com/in/aome510/}{\faIcon{linkedin} aome510}
  & \href{mailto:phamducthang1234@gmail.com}{\faIcon{envelope} phamducthang1234@gmail.com}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeHeading
  {University of Waterloo}{Waterloo, Canada}
  {Candidate for Honours Bachelor in Computer Science, Co-op}{Sep 2019 - May 2023 (expected)}
  \resumeListStart
    \resumeSubItem{Cumulative GPA}{92\%.}
    \resumeSubItem{Michael and Ophelia Lazaridis Olympiad Scholarship}{
      \resumeListStart
      \vspace{-5pt}
        \resumeDescItem{Recipient of the Faculty of Mathematics' Olympiad Scholarship that covers full tuition and living expenses.}
      \resumeListEnd
    }
  \resumeListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeListStart
    \resumeSubheading
      {Curvegrid}{Tokyo, Japan}
      {Blockchain Software Engineer}{May 2021 - Sep 2021}
      \resumeListStart
        \resumeDescItem{Designed and developed a reference implementation of MultiBaas Bridge, a cross-chain portal that allows fast and secure movement of digital assets across different blockchain platforms.}
        \resumeDescItem{Added smart contract integrations to allow MultiBaas Bridge server to operate the cross-chain movement of ERC20 and ERC721 tokens with off-chain relayers.}
        \resumeDescItem{Worked on migrating the company's front-end stack from Vuetify 1 with Javascript to Vuetify 2 with Typescript and upgrading the back-end API system from v0 to v1.}
      \resumeListEnd

    \resumeSubheading
      {Curvegrid}{Tokyo, Japan}
      {Blockchain Software Engineer}{May 2020 - Sep 2020}
      \resumeListStart
        \resumeDescItem{Maintained a Golang back-end server that interacts with the blockchain via REST APIs.}
        \resumeDescItem{Implemented new event and address tables using Vue.js to manage blockchain data with a web-based control panel.}
      \resumeListEnd

    \resumeSubheading
      {VinAI Research}{Hanoi, Vietnam}
      {ML Engineer Intern}{May - Sep 2019}
      \resumeListStart
        \resumeDescItem{Developed a deep learning project for quantifying the percentage of people wearing masks on the street in real-time.}
        \resumeDescItem{Trained a custom model using the \href{https://github.com/mahyarnajibi/SSH}{\linkDesc{SSH model}} for face detection and a Resnet50 model for masked face classification.}
        \resumeDescItem{Achieved 96.5\% accuracy during inference and an average real-time performance of 10-15 FPS.}
        \resumeDescItem{Source code: \href{https://github.com/aome510/Mask-Classifier}{\linkDesc{https://github.com/aome510/Mask-Classifier}}.}
      \resumeListEnd
  \resumeListEnd

%-----------Awards-----------------
\section{Awards}
  \resumeListStart
    \resumeSubheading{ICPC East Central North America Regional Contest}{Windsor, Canada}{Gold Medalist - \href{https://ecna19.kattis.com/standings}{\linkDesc{Ranked 2/105}}}{ Oct 2019}
    \resumeSubheading{International Olympiad in Informatics}{Tsukuba, Japan}{Gold Medalist - \href{http://stats.ioinformatics.org/people/6729}{\linkDesc{Ranked 10/336}}}{Sep 2018}
    \resumeSubheading{Asia-Pacific Olympiad in Informatics}{Hanoi, Vietnam}{Gold Medalist - \href{http://apio-olympiad.org/2018/results.html}{\linkDesc{Ranked 12/187}}}{May 2018}
  \resumeListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeListStart
    \resumeItem{\href{https://github.com/aome510/hackernews-TUI}{\linkDesc{Hacker News TUI}}}
    {\vspace{-5pt}
      \resumeListStart
      \resumeDescItem{Used Rust to build a fast and configurable terminal application for reading Hacker News articles and discussions.}
      \resumeDescItem{Hit the \href{https://news.ycombinator.com/item?id=26929588}{\linkDesc{front-page}} of Hacker News during the first official release.}
    \resumeListEnd}
    \vspace{-5pt}
    \resumeItem{\href{https://github.com/aome510/spotify-player}{\linkDesc{Spotify Player}}}
    {\vspace{-5pt}
      \resumeListStart
      \resumeDescItem{Developed a command driven player in Rust to control Spotify and listen to music on the terminal.}
    \resumeListEnd}
    \vspace{-5pt}
    \resumeItem{\href{https://github.com/aome510/Generating-Anime-Music}{\linkDesc{Anime Music Generator}}}
    {\vspace{-5pt}
      \resumeListStart
      \resumeDescItem{Used Tensorflow to train a bidirectional recurrent neural network that generates classical anime songs and deployed it to Heruko as a simple Django web app.}
    \resumeListEnd}
    \vspace{-5pt}
  \resumeListEnd

% --------SKILLS------------
\section{Skills}
  \resumeListStart
    \resumeSubItem{Languages}{Rust, Golang, Typescript/Javascript, C/C++, Python, Scala, SQL}
    \resumeSubItem{Technologies}{Vue.js, Node.js, Pytorch, Tensorflow}
    \resumeSubItem{Tools}{Unix/Linux, Git, PostgreSQL, Docker, Github actions}
  \resumeListEnd

%-------------------------------------------
\end{document}
